Alex's Notes and Text Fragments for the JSS Manuscript

### 2021-06-27 paper/paper.Rmd
minor
group level vs custom cv

### Group-Level CV

@@

<!-- FIXME: eval=TRUE when available upstream im mlr3 -->
<!-- FIXME: add visualization when method is available -->

@@

>>>>

### Group-level resampling

@@

FIXME: eval=TRUE when available upstream im mlr3
FIXME: add visualization when method is available

@@

<!-- group level CV vs custom CV -->
\pkg{mlr3spatiotempcv} supports two factor-based partitioning schemes: "group-level resampling" and "custom resampling".
Both are similar in that they require external user input for partition creation, i.e. a factor variable which assigns all observations into a distinct group.
While this the entire idea of "custom resampling" and each group becomes a test set in the CV, "group-level resampling" methods apply additional aggregation on top of these initial groups: for example, users can supply an integer value to an argument named `fold` in the LLO method (e.g. `5L`) which combines the initial groups (e.g. $n = 20$) into their final fold-level partitions, which would result in four groups per partition [@meyer2018].
The important point is that observations from within one group will either be assigned to the train or test set and never be split up.
"Group-level resampling" can be, in contrast to "custom resampling", repeated multiple times because multiple different aggregations are possible in theory.
However, it also requires the amount of initial groups to be substantially higher than the amount of folds so that a sensible aggregation is possible in the first place.
